MG7: Configurable and scalable 16S data analysis

### 2016-07-25 docs/mg7-paper/out/paper.tex
cite bio4j again

\begin{itemize}
\tightlist
\item
  Static reproducible specification of dependencies and behavior of the
  different components using \emph{\protect\hyperlink{statika}{Statika}}
  and \emph{\protect\hyperlink{datasets}{Datasets}}
\item
  Parallelization and distributed analysis based on AWS, with on-demand
  infrastructure as the basic paradigm
\item
  Definition of complex workflows using
  \emph{\protect\hyperlink{loquat}{Loquat}}, a composable system for
  scaling/parallelizing stateless computations especially designed for
  AWS
\item
  A new approach to data analysis specification, management and
  specification based on working with it in exactly the same way as for
  a software project, together with the extensive use of compile-time
  structures and checks
\item
  Modeling of the taxonomy tree using the new paradigm of graph
  databases (Bio4j). It facilitates the taxonomic assignment tasks and
  the calculation of the taxa abundance values considering the
  hierarchic structure of taxonomy tree (cumulative values)
\item
  Exhaustive per-read taxonomic assignment using two complementary
  assignment algorithms Lowest Common Ancestor and Best BLAST Hit
\item
  Using a new 16S database of reference sequences (16S-DB7) with a
  flexible and sustainable system of updating and project-driven
  customization
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  Static reproducible specification of dependencies and behavior of the
  different components using \emph{\protect\hyperlink{statika}{Statika}}
  and \emph{\protect\hyperlink{datasets}{Datasets}}
\item
  Parallelization and distributed analysis based on AWS, with on-demand
  infrastructure as the basic paradigm
\item
  Definition of complex workflows using
  \emph{\protect\hyperlink{loquat}{Loquat}}, a composable system for
  scaling/parallelizing stateless computations especially designed for
  AWS
\item
  A new approach to data analysis specification, management and
  specification based on working with it in exactly the same way as for
  a software project, together with the extensive use of compile-time
  structures and checks
\item
  Modeling of the taxonomy tree using the new paradigm of graph
  databases (Bio4j, \citep{pareja2015bio4j}). It facilitates the
  taxonomic assignment tasks and the calculation of the taxa abundance
  values considering the hierarchic structure of taxonomy tree
\item
  Exhaustive per-read taxonomic assignment using two complementary
  assignment algorithms Lowest Common Ancestor and Best BLAST Hit
\item
  Using a new 16S database of reference sequences (16S-DB7) with a
  flexible and sustainable system of updating and project-driven
  customization
\end{itemize}
